Details of specific functions

### 2021-03-26 inst/gitbook/03_specific-tutorials.Rmd
added things to tutorial

Since the package's version 1.5.10, trees can be directly att

>>>>

Since the package's version 1.5.10, trees can be directly attached to `dispRity` objects.
This allows any function in the package that has an input argument called "`tree`" to automatically intake the tree from the `dispRity` object.
This is especially useful for disparity metrics that requires calculations based on a phylogenetic tree (e.g. `ancestral.dist` or `projections.tree`) and if phylogeny (or phylogenie\*s\*) are going to be an important part of your analyses.

Trees are attached to `dispRity` object as soon as they are called in any function of the package (e.g. as an argument in `chrono.subsets` or in `dispRity`) and are stored in `my_dispRity_object$tree`.
You can always manually attach, detach or modify the tree parts of a `dispRity` object using the utility functions `get.tree` (to access the trees), `remove.tree` (to remove it) and `add.tree` (to... add trees!).
The only requirement for this to work is that the labels in the tree must match the ones in the data.
If the tree has node labels, their node labels must also match the data.
Similarly if the data has entries for node labels, they must be present in the tree.

Here is a quick demo on how attaching trees to `dispRity` objects can work and make your life easy: for example here we will measure how the sum of branch length changes through time when time slicing through some demo data with a acctran split time slice model (see more info [here](#chrono-subsets)).

```{r}
## Loading some demo data:
## An ordinated matrix with node and tip labels
data(BeckLee_mat99)
## The corresponding tree with tip and node labels
data(BeckLee_tree)
## A list of tips ages for the fossil data
data(BeckLee_ages)

## Time slicing through the tree using the equal split algorithm
time_slices <- chrono.subsets(data   = BeckLee_mat99,
                              tree   = BeckLee_tree,
                              FADLAD = BeckLee_ages,
                              method = "continuous",
                              model  = "acctran",
                              time   = 15)

## We can visualise the resulting trait space with the phylogeny
## (using the specific argument as follows)
plot(time_slices, type = "preview",
     specific.args = list(tree = TRUE))
## Note that some nodes are never selected thus explaining the branches not reaching them.
```

And we can then measure disparity as the sum of the edge length at each time slice on the bootstrapped data:

```{r}
## Measuring the sum of the edge length per slice
sum_edge_length <- dispRity(boot.matrix(time_slices), metric = c(sum, edge.length.tree))
## Summarising and plotting
summary(sum_edge_length)
plot(sum_edge_length)
```

Of course this can be done with multiple trees and be combined with an approach using multiple matrices (see [here](#multi.input))!
